Report for the Deep Learning Course Assignment 3

### 2016-12-16 practical_3/report/report_methenitis.tex
updated with transfer learning

\subsection{One-vs-Rest Classifier}
\begin{itemize}
\textbf{Experiment 1}: $0.476$
\textbf{Experiment 2}: $0.473$
\textbf{Experiment 3}: $0.682$
\end{itemize}

%Figure~\ref{fig:6} illustrates the loss in the training and the test set using the normal implementation of the batch creation.
%The siamese network learning converges after $12000$ steps.
%The network seems to learn the features that minimize the loss.
%Figure~\ref{fig:7} presents four different implementations using different parameters.
%
%
%\begin{figure}[h!]
%\centering
%\includegraphics[width=7.2cm]{loss-siamese-train-1.png}\	
%\includegraphics[width=6.6cm]{loss-siamese-test-1.pdf}
%\caption{Loss in the training (Left) and the test set (Right - green line) for $15000$ training steps, $margin = 0.2$, and weight regularization loss.}
%\label{fig:6}
%\end{figure}
%
%
%\begin{figure}[h!]
%\centering
%\includegraphics[width=0.4\textwidth]{loss-siamese-train-1}
%\includegraphics[width=0.4\textwidth]{loss-siamese-train-2}
%\includegraphics[width=0.4\textwidth]{loss-siamese-train-3}
%\includegraphics[width=0.4\textwidth]{loss-siamese-train-4}
%\caption{Visualization of the $l2$-normalized features in the output of the CNN for $5000$ samples of the test set. For $margin=0.2$ with weight normalization (top-left), for $margin=1.0$ with weight normalization (top-right), and without normalization (bottom-left). Last, the visualization of the features when the alternative way of creating batches is used (bottom-right).
%For $margin=1.0$ the alternative way of creating batches is reducing the loss.}
%\label{fig:7}
%\end{figure}
%
%
%\subsection{Feature Visualization}
%
%
%Using the same TSNE algorithm we present the $2$-dimensional representation of the features for the siamese architecture. Figure~\ref{fig:8} presents the $2$-d representation of the features over $5000$ samples of the test set, for the four different implementation showed in Figure~\ref{fig:7}.
%
%\begin{figure}[h!]
%\centering
%\includegraphics[width=0.4\textwidth]{visualization-siamese-features_fc2.pdf}
%\includegraphics[width=0.4\textwidth]{visualization-siamese-features_fc2-1.pdf}
%\includegraphics[width=0.4\textwidth]{visualization-siamese-features_fc2-2.pdf}
%\includegraphics[width=0.4\textwidth]{visualization-siamese-features_fc2-3.pdf}
%\caption{Visualization of the $l2$-normalized features in the output of the CNN for $5000$ samples of the test set. For $margin=0.2$ with weight normalization (top-left), for $margin=1.0$ with weight normalization (top-right), and without normalization (bottom-left). Last, the visualization of the features when the alternative way of creating batches is used $margin = 1.0$ and without weight normalization (bottom-right).}
%\label{fig:8}
%\end{figure}
%
%\subsection{One-vs-All Classifiers}
%
%For the four different implementation parameters that were presented in the Figure~\ref{fig:7} and \ref{fig:8} the accuracy of the one-vs-all classifier that is achieved:
%\begin{itemize}
%\item Accuracy with l\_2-norm: $0.0957$
%\item Accuracy with l\_2-norm: $0.121$
%\item Accuracy with l\_2-norm: $0.1048$
%\item Accuracy with l\_2-norm: $0.1564$
%\end{itemize}
%I showed that the loss was reduced by using the alternative way of sampling batches, here the accuracy of the classifier is increased as well.
%Figure
%
%
%\subsection{Update for Task 2}
%
%In this section I provide the results of a last experiment where I used $50000$ training steps.
%The model seems to learn and distinguishes between different classes.
%Figure~\ref{fig:9} presents the loss in the training set.
%
%
%
%\begin{figure}[h!]
%\centering
%\includegraphics[width=0.8\textwidth]{loss-siamese-final.png}
%\caption{Loss of the siamese architecture of the CNN in the training procedure for $50000$ training steps. For $margin=1.0$ without weight normalization.}
%\label{fig:9}
%\end{figure}
%
%Figure~\ref{fig:10} presents the visualized in $2-d$ features.
%
%\begin{figure}[h!]
%\centering
%\includegraphics[width=0.8\textwidth]{visualization-siamese-features_fc2-4.pdf}
%\caption{Visualization of the $l2$-normalized features in the output of the CNN for all samples of the test set. For $margin=1.0$ without weight normalization.}
%\label{fig:10}
%\end{figure}
%
%To test the accuracy of the one-vs-all classifier I use the features retained by the learned model to train the classifiers.
%Using the 80 percent of the features I train a linear kernel OneVsRest classifier, and test the accuracy over the rest 20 percent.
%The reported accuracy over the test set is:
%\begin{itemize}
%\item Accuracy with l\_2-norm: $0.6789$
%\end{itemize}
%
%
%
%\section{Conclusion}
%
%In this assignment I implemented a CNN and reported its performance over the CIFAR10 dataset using different parameters.
%I also implemented the siamese architecture which uses two versions of the same CNN to perform learning in order to distinguish between classes.
%The amount of training steps requires for the siamese are higher than the single CNN architecture.
%The time required for the experiments did not let me try more parameter values, therefore I cannot draw any important conclusions regarding the right parameters that should be used for the two different approaches.

>>>>

\subsection{One-vs-Rest Classifier}
Here, I present the accuracy of the one-vs-rest classifier on the features learned from in the final layer of the siamese network for all experiments
\begin{itemize}
\item \textbf{Experiment 1}: $0.476$
\item \textbf{Experiment 2}: $0.473$
\item \textbf{Experiment 3}: $\mathbf{0.682}$
\end{itemize}

\section{Transfer Learning}

 \begin{figure}[h!]
\centering
\includegraphics[width=5.2cm]{graph.png}
\caption{Graph for the task 3 of the assignment, the final three layers of convnet were used. Note the stop gradient operation, where we don't want to update the pre-trained weights.}
\label{fig:features}
\end{figure}

%
%Using the same TSNE algorithm we present the $2$-dimensional representation of the feat
%\section{Conclusion}
%
%In this assignment I implemented a CNN and reported its performance over the CIFAR10 dataset using different parameters.
%I also implemented the siamese architecture which uses two versions of the same CNN to perform learning in order to distinguish between classes.
%The amount of training steps requires for the siamese are higher than the single CNN architecture.
%The time required for the experiments did not let me try more parameter values, therefore I cannot draw any important conclusions regarding the right parameters that should be used for the two different approaches.
